---
title: "Econanalysis"
author: Tanvi Chiddarwar
date: 06/08/2021
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Econanalysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Econanalysis)
```


# Package Econanalysis 

This package includes functions to automate analysis of Economic Datasets from the FRED website. These functions are specialized to work with specifically these datasets. 

## Function Tutorials 

In the following section we will look at some of these functions in action

### gdp_analysis and debt_analysis

It is important to have the right dataset in order to use this function as the variables are specific to the ones used on the FRED website. 


```{r}
# Where gdp is the GDP dataset over time from FRED 

gdp_analysis(gdp)

# Where debt is the Public debt dataset over time from FRED 

debt_analysis(debt)
```


## debt_gdp_analysis

This function combines the public debt dataset and GDP dataset using join by date. It then plots both of them on the same graph. 

```{r}
debt_gdp_analysis(debt, gdp)
```

## percent_change 

This function creates a new column in the dataset that shows the percent change over the years. 
This new variable will be labelled $pct_change$

In this example we will create a new column in the unemployment dataset which will be the change in unemployment rate over the years. We will save this back into the dataset. 
```{r}
unemp <- percent_change(unemp, UNRATE)
```


## okuns_law

This function allows to use FRED datasets to see if Okun's Law of the relationship between change in GDP and unemployment rate applies in real life.  

Once the datasets are specified, a summary of the linear regression and a plot are returned back. 

```{r}
okuns_law(gdp, unemp)
```


## philips

This function allows to use FRED datasets to create Philip's Curve of the inflation rate versus the unemployment rate. 

Once the datasets are specified, they are combined using a join and then a plot depicting the relationship between the two is returned. 

```{r}
philips(infl, unemp)
```


